---
title: "Immigration to Canada analysis"
author: "Shanmukh Santosh Chintakula, Haomin Wang"
output:
  html_document:
    fig_width: 8
    code_folding: hide
    highlight: tango
    toc: yes
    toc_float:
      collapsed: yes
  pdf_document:
    toc: yes
editor_options:
  markdown:
    wrap: 72
---

## Introduction

> "The simple graph has brought more information to the data analyst's
> mind than any other device." --- John Tukey

## Objective

### Prerequisites

Store the Canada immigration dataset into variable data

```{r setup, message=FALSE, warning=FALSE}
data <- read.csv("https://raw.githubusercontent.com/jaime-wang/CS544-project-Haomin-Shanmukh/main/canadian_immegration_data.csv")

```

Install all the packages required

```{r eval = FALSE,message=FALSE, warning=FALSE}
install.packages("corrplot")
install.packages("ggplot2")
install.packages("ggrepel")
install.packages("ggpubr")
tinytex::install_tinytex()
```

Load the packages we need

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(corrplot)
library(RColorBrewer)
library(sampling)
library(rgl)
library(ggrepel)
library(tidyverse)
library(ggthemes)
library(sampling)
library(ggpubr)
```

## First step : preprocess the dataset

The dataset of the Canada immigration has some columns to be modified. The data type of column name about years should be tranformed into decimal from string, for example, from "X1980" to "1980".
Also, the total number of the immigrants is from each country in the original dataset. If we need the total number from each continent, we use aggregate function to get counts and the aggregations of the information. New data frames or vectors were created to store this information.
Turn original data "United Kingdom of Great Britain and Northern Ireland" into abbreviation "UK", so that the plots will be better organized.

```{r message=FALSE, warning=FALSE}
colnames(data)[5:38] <- 1980:2013
df_Continent <- aggregate(data$Total,data["Continent"],sum)
colnames(df_Continent)[2] <- "Total"
data[data$Country == "United Kingdom of Great Britain and Northern Ireland", "Country"] <- "UK"
```

## Total immigrants to Canada from 5 continents

To understand where most Canadian immigrants come from, we draw a Barplot of the total immigrants from each continent.
It is evident from the graph that the largest number of people are from Asia, and the least are from Oceania.
The total number from Asia reaches 3.3 million, which is a very exaggerating number.

```{r message=FALSE, warning=FALSE}
p <- ggplot(data = df_Continent,
            mapping = aes(
              x = Continent, 
              y = Total, 
              fill = Continent))
p + geom_col() +
  guides(fill=FALSE)+coord_flip()+labs(y="Immigrants")
```

## Distribution of the immigrants

In order to find the precise distribution of the number of immigrants, we use a pie chart to show the distribution of immigrants from each continent. We can find that Asia occupies 51.77%, more than half of the total. Europe accounted for 22.01%, which is also a large part. Latin America accounted for 11.94%, Africa and North America accounted for 9.66% and 3.76% respectively, Oceania accounted for the least, only 0.86%. So people from Asia and Europe are more likely to immigrate to Canada.

```{r message=FALSE, warning=FALSE}
whole <- sum(df_Continent$Total);
df2 <- df_Continent %>% 
  mutate(csum = rev(cumsum(rev(Total))), 
         pos = Total/2 + lead(csum, 1),
         pos = if_else(is.na(pos), Total/2, pos))

ggplot(df_Continent, aes(x = "" , y = Total, fill = fct_inorder(Continent))) +
  geom_col(width = 1) +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "Pastel1") +
  geom_label_repel(data = df2,
                   aes(y = pos, label = paste0(round(Total/whole*100,2), "%")),
                   size = 4.5, nudge_x = 1, show.legend = FALSE) +
  guides(fill = guide_legend(title = "Continent")) +
  theme_void()
```

## TOP 5 countries

To how the immigrants number varies from year 1980 to 2013, here is a Line chart of Top 5 countries immigrants each year.It can be found that the number in China is increasing overall, but it peaked at about 35,000 people a year in about 2005 and then began to decline. India's figures show a trend of flat growth, at most about 30,000 a year.Pakistan's data grew to about 15,000 people in 2000 and then began to decline.Philipplines figures rose sharply from around 10,000 a year in 2000 to nearly 40,000 a year in 2013. Figures for the UK grew from 1980 to around 30,000 per year in 1990, then dropped sharply to around 5,000 per year in 2005 before starting to grow again. We can probably speculate that the Philippines' figures will continue to grow beyond 2013.

```{r message=FALSE, warning=FALSE}
df_top <- data[order(data$Total,decreasing = TRUE),]
df_year <- data %>% select(-Total) %>% gather(key = "Year", value = "No_of_Immigrants", -c(Country, Continent, Region, DevName))
data_2 <- data %>% select(-Total) %>% gather(key = "Year", value = "No_of_Immigrants", -c(Country, Continent, Region, DevName))
x <- data_2 %>% filter(Country %in% df_top[1:5,"Country"])

ggplot(x, aes(Year, No_of_Immigrants, color= Country, group= Country)) + 
  geom_smooth(se= FALSE) + 
  labs(title = "Immigration pattern of Top 5 Countries", y = "Immigrants") +
  theme_economist(base_size = 22 ) +
  theme(axis.text.x = element_text(hjust = 1, vjust = 0.3)) + 
  theme(axis.text.y = element_text(hjust = 1.6)) +
  theme(axis.title.y = element_text(family = "serif", size = 14, face= "italic", hjust = 0.3 ,vjust= 0.5), legend.position = "right") +
  theme(axis.title.x = element_text(family = "serif", size = 14, face= "italic")) +
  theme(plot.title = element_text(family = "serif", size = 18, hjust = 0.5)) +
  theme(legend.title = element_text(family = "serif", size = 14, face = "bold")) +
  theme(legend.text = element_text(family = "serif", size = 12, face = "italic")) +
  scale_x_discrete(breaks= c(1980, 1990, 2000, 2010))
```

## TOP 10 countries immigrants

To find out how the immigrants number varies per year in some specific countries, we plot a Boxplot of immigrants from 10 top countries. We can find a wide range of data variation for China, India and UK. Some countries like usa, sri lanka, korea and poland have small changes in the data, indicating that these countries are stable and some people immigrate to Canada

```{r message=FALSE, warning=FALSE}
df_top <- data[order(data$Total,decreasing = TRUE),]
top_10 <- df_top[1:10,"Country"]
data_3 <- data_2 %>% filter(Country %in% top_10)
ggplot(data_3, aes(Country, No_of_Immigrants, color= Country, group= Country)) + geom_boxplot()+coord_flip()+
ylab("Number of immigrants per year")+labs(title ="TOP 10 Countries immigrants per year")
```

## Developing region vs developed Region immigration

Line chart of immigrants from developing Region and developed region

```{r message=FALSE, warning=FALSE}
df_year %>% group_by(DevName, Year) %>% summarise(Total_Immigrants = sum(No_of_Immigrants)) %>%
  ggplot(aes(Year, Total_Immigrants, fill= DevName, group= DevName)) +
  geom_area(size=0, alpha = 0.7, color= "white") +
  theme_economist(base_size = 22 ) +
  labs(title = "Developing vs Developed Region Immigration", y = "Total Immigrants") +
  theme(axis.text.x = element_text(angle = 90, hjust = 10, vjust = 0.3, size = 8)) + 
  theme(axis.text.y = element_text(hjust = 1.6)) +
  theme(axis.title.y = element_text(family = "A", size = 12, face= "bold", hjust = 0.3 ,vjust= 1.5), legend.position = "right") +
  theme(axis.title.x = element_text(family = "A", size = 12, face= "bold")) +
  theme(plot.title = element_text(family = "A", size = 18, hjust = 0.4)) +
  theme(legend.title = element_text(family = "A", size = 9, face = "bold")) +
  theme(legend.text = element_text(family = "A", size = 7, face = "bold"))+scale_fill_brewer(palette="Dark2")
```

## CLT
## CLT on total migration for countries.
```{r message=FALSE, warning=FALSE}
samples <- 1000


s10<-10
xbar10 <- numeric(samples)
set.seed(123)
for (i in 1:samples) {
  xbar10[i] <- mean(data$Total[which(srswor(s10, nrow(data))==1)])
}

size10<- ggplot() + geom_histogram(aes(x= xbar10, y=..density..), fill="lightskyblue", colour="navy blue"  , bins = 30) +
  ggtitle("Sample Size = 10")

cat("Sample Size = ", s10, " Mean = ", mean(xbar10),
    " SD = ", sd(xbar10), "\n")

s25<-25
xbar25 <- numeric(samples)
set.seed(123)
for (i in 1:samples) {
  xbar25[i] <- mean(data$Total[which(srswor(s25, nrow(data))==1)])
}

size25<- ggplot() + geom_histogram(aes(x= xbar25, y=..density..), fill="lightskyblue", colour="navy blue"  , bins = 30) +
  ggtitle("Sample Size = 25")


cat("Sample Size = ", s25, " Mean = ", mean(xbar25),
    " SD = ", sd(xbar25), "\n")


s45<-45
xbar45 <- numeric(samples)
set.seed(123)
for (i in 1:samples) {
  xbar45[i] <- mean(data$Total[which(srswor(s45, nrow(data))==1)])
}

size45<- ggplot() + geom_histogram(aes(x= xbar45, y=..density..), fill="lightskyblue", colour="navy blue"  , bins = 30) +
  ggtitle("Sample Size = 45")

cat("Sample Size = ", s45, " Mean = ", mean(xbar45),
    " SD = ", sd(xbar45), "\n")


s70<-70
xbar70 <- numeric(samples)
set.seed(123)
for (i in 1:samples) {
  xbar70[i] <- mean(data$Total[which(srswor(s70, nrow(data))==1)])
}

size70<- ggplot() + geom_histogram(aes(x= xbar70, y=..density..), fill="lightskyblue", colour="navy blue"  , bins = 30) +
  ggtitle("Sample Size = 70") 

cat("Sample Size = ", s70, " Mean = ", mean(xbar70),
    " SD = ", sd(xbar70), "\n")

ggarrange(size10, size25, size45, size70 , 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
```


## Sampling
```{r message=FALSE, warning=FALSE}
###Population
barplot(table(data$Continent), las=2, col = "lightskyblue")


##Systematic Sampling
set.seed(195)
#

N <- nrow(data)
n <- 39
k <- ceiling(N / n)
r <- sample(k, 1)
s <- seq(r, by = k, length = n)

sample.1 <- data[s, ]
nrow(sample.1)
barplot(table(sample.1$Continent), las=2, col = "lightskyblue")


# Stratified, unequal sized strata
set.seed(195)
section.ids <- rep(LETTERS[1:4], c(10, 20, 30, 40))

section.scores <- round(runif(100, 60, 80))

df <- data.frame(data$Continent, data$DevName, data$Total)

head(df)

freq <- table(data$DevName)
freq

st.sizes <- round(39 * freq / sum(freq))
st.sizes

st.2 <- sampling::strata(df, stratanames = c("data.DevName"),
                         size = st.sizes, method = "srswor",
                         description = TRUE)

nrow(st.2)

st.sample2 <- getdata(df, st.2)
st.sample2
barplot(table(st.sample2$data.Continent),  las=2, col = "lightskyblue")


# srswor

s <- srswor(39, nrow(df))

sample.3 <- df[s != 0, ]
head(sample.3)
barplot(table(sample.3$data.Continent), las=2, col = "lightskyblue")
```

### Conclusion
